```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Interactions between continuous variables

```{r}
# make a linear model with the two continuous predictor variables interacting
# Let's say the relationship between elk density and canopy height is mediated by
# wolf density
# I.e., when wolves are scarce, elk like open fields (low canopy height). But when
# wolves are plentiful, elk get scared and retreat to forests (high canopy height) 
# to hide
set.seed(54321)
canopy_height <- rnorm(1e3, 100, sd = 10) #random var for canopy height
wolf_density <- rnorm(1e3, 3, sd = 0.5) # random var for wolf density, wolf/km^2
```

```{r}
# normal distribution of canopy heights
ggplot(tibble(canopy_height), aes(canopy_height)) + geom_histogram()

# normal distribution of wolf density
ggplot(tibble(wolf_density), aes(wolf_density)) + geom_histogram()
```


```{r}
# Arbitrarily choose coefficients
beta0 <- 175  # Intercept
beta1 <- 3.0  # Coefficient for canopy height
beta2 <- -0.2 # Coefficient for wolf density
beta3 <- -1.0 # Coefficient for canopy height X wolf density

# Simulate!
elk_density <- beta0 + beta1 * canopy_height + beta2 * wolf_density + 
  beta3 * canopy_height * wolf_density + rnorm(1e3, sd = 0.5) # last factor is random noise

# Visualize
yellowstone <- tibble(canopy_height, wolf_density, elk_density)
ggplot(yellowstone, aes(canopy_height, elk_density, color = wolf_density)) +
  geom_point(shape = 21) +
  scale_color_distiller(palette = "Reds", direction = 1) +
  theme_classic()
```

```{r}
# Fit the model
yellowstone_mod <- lm(
  elk_density ~ canopy_height + wolf_density + canopy_height : wolf_density,
  yellowstone
)
summary(yellowstone_mod)
```
Wolves --> less elk --> less grazing --> more canopy 

elk = beta0 + beta1Canopy + beta2wolf + beta3(Canopy x Wolf)

elk = beta0 + (beta1 + beta3)Canopy + beta2Wolf

Beta3 is neg because, decreasing elk density, every increase in the interaction between the two brings elk down by one unit.

Canopy height and elk density. Lower canopy

What's the $\hat{y}$ line for low, medium, and high wolf densities?

```{r}
# Model coefficients
beta0_hat <- coef(yellowstone_mod)[1]
beta1_hat <- coef(yellowstone_mod)[2]
beta2_hat <- coef(yellowstone_mod)[3]
beta3_hat <- coef(yellowstone_mod)[4]
prediction <- expand_grid( # gives you all the combos of vectors
  canopy_height = seq(70, 130, length.out = 5), # 5 canopy heights
  wolf_density = c(1.5, 3, 4.5) # 3 wolf densities
) %>% # means 15 total observations
  mutate(yhat = beta0_hat + beta1_hat * canopy_height + beta2_hat * wolf_density +
           beta3_hat * canopy_height * wolf_density)

ggplot(yellowstone, aes(canopy_height, elk_density, color = wolf_density)) +
  geom_point(shape = 21) +
  scale_color_distiller(palette = "Reds", direction = 1) +
  geom_line(aes(y = yhat, group = wolf_density), prediction, linewidth = 2) +
  theme_classic()
```

Questions:
Darker red-->less wolves. 
* Where would the line for wolf density = 4 be? How about wolf density = 2?


* What's the slope of canopy height when wolf density is 1.5, 3, and 4.5?
